Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-26 documentation/paper.tex
Finished filling out supervised learning tables

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Using the same network architecture (except for the input layer), and still without $WallCut(D)$, $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with this configuration was 91\% (although with a relatively high class-wise standard deviation of 0.61). While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConvWithPos(\omega, \chi)$ with $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Layers $\times$ & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0.003 & 0 & 24 & 3 & 3 & 95\% & 99\% & 94\% & 0.44 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1533824431_epoch30.json
            \hline
            0.003 & 0 & 48 & 5 & 3 & 96\% & 99\% & 96\% & 0.41 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533825716_epoch43.json
            \hline
            0.003 & 0.5 & 24 & 5 & 3 & 93\% & 98\% & 92\% & 0.50 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1533828588_epoch27.json
            \hline
            0.001 & 0 & 48 & 5 & 3 & 95\% & 98\% & 95\% & 0.48 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533832229_epoch16.json
            \hline
            0.001 & 0.25 & 48 & 3 & 6 & 93\% & 94\% & 97\% & 0.62 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters48_kernel_size3_convolutional_layers_per_group6time1533834812_epoch30.json
            \hline
            0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 97\% & 97\% & 0.49 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group6time1533849077_epoch45.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConvWithPos(\omega, \chi)$ without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Layers $\times$ & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0.003 & 0 & 24 & 3 & 3 & 91\% & 95\% & 78\% & 0.61 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1532800009_epoch78.json
            \hline
            0.003 & 0.5 & 24 & 5 & 3 & 91\% & 95\% & 78\% & 0.65 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1532813246_epoch49.json
            \hline
            0.001 & 0.25 & 24 & 3 & 3 & 91\% & 88\% & 84\% & 0.66 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1532825383_epoch88.json
            \hline
            0.001 & 0.5 & 48 & 5 & 3 & 88\% & 92\% & 73\% & 0.73 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.001_dense_dropout0.5_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1532837124_epoch0.json
            \hline
            0.0003 & 0 & 48 & 5 & 6 & 78\% & 76\% & 56\% & 0.95 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.0003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group6time1532846835_epoch63.json
            \hline
            0.0003 & 0.5 & 48 & 5 & 6 & 74\% & 67\% & 53\% & 0.92 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters48_kernel_size5_convolutional_layers_per_group6time1532863869_epoch10.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of supervised learning configurations, trained with $WallCut(D)$.}
        \begin{tabular}{|l|l|l|}
            \hline
            Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
            \hline
            $FourierMLP(PosCor(\beta_{8}), \chi)$ & 97\% & 0.42 \\
            \hline
            $FourierMLP(\beta_{8})$ & 98\% & 0.29 \\
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 95\% & 0.44 \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 94\% & 0.52 \\
            \hline
            $FourierMLPWithPos(\beta_{40}, \chi)$ & 91\% & 0.54 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 91\% & 0.53 \\
            \hline
            Original PICO-60 Neural Network & 94\% & 0.99 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of supervised learning configurations, trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|}
            \hline
            Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 0.63 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 97\% & 0.47 \\
            \hline
            $DeepConv(\omega)$ & 77\% & 0.86 \\
            \hline
            $DeepConvWithPos(\omega, \chi)$ & 91\% & 0.61 \\
            \hline
            $ImageConv(\iota)$ & 85\% & 0.95 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

>>>>

Once the audio was cropped properly, $DeepConv(\omega)$ achieved a maximum of 77\% accuracy on validation data. Errors were not balanced at all; precision was 76\% and recall was 94\%, indicating that the network was overzealous to classify particles as neutrons. Using the same network architecture (except for the input layer), and still without $WallCut(D)$, $DeepConvWithPos(\omega, \chi)$ achieved 85\%. The maximum obtained on a grid search with this configuration was 91\%, although with a relatively high class-wise standard deviation of 0.61. Precision improved greatly, reaching 95\%, while recall was reduced, at a maximum of 84\%. While this is not a drastic improvement, it is a fairly strong indication that the network is able to extract meaningful information from the position, which may be used in an internal position correction of the volume.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConvWithPos(\omega, \chi)$ with $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Conv Layers & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0.003 & 0 & 24 & 3 & 17 & 95\% & 99\% & 94\% & 0.44 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1533824431_epoch30.json
            \hline
            0.003 & 0 & 48 & 5 & 17 & 96\% & 99\% & 96\% & 0.41 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533825716_epoch43.json
            \hline
            0.003 & 0.5 & 24 & 5 & 17 & 93\% & 98\% & 92\% & 0.50 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1533828588_epoch27.json
            \hline
            0.001 & 0 & 48 & 5 & 17 & 95\% & 98\% & 95\% & 0.48 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1533832229_epoch16.json
            \hline
            0.001 & 0.25 & 48 & 3 & 32 & 93\% & 94\% & 97\% & 0.62 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters48_kernel_size3_convolutional_layers_per_group6time1533834812_epoch30.json
            \hline
            0.0003 & 0.5 & 24 & 5 & 32 & 95\% & 97\% & 97\% & 0.49 \\
            % ../experimental_data/validation_results/2018_08_09_waveform_grid_search_with_wall_cuts/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group6time1533849077_epoch45.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConvWithPos(\omega, \chi)$ without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Conv Layers & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0.003 & 0 & 24 & 3 & 17 & 91\% & 95\% & 78\% & 0.61 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.003_dense_dropout0_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1532800009_epoch78.json
            \hline
            0.003 & 0.5 & 24 & 5 & 17 & 91\% & 95\% & 78\% & 0.65 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.003_dense_dropout0.5_first_layer_filters24_kernel_size5_convolutional_layers_per_group3time1532813246_epoch49.json
            \hline
            0.001 & 0.25 & 24 & 3 & 17 & 91\% & 88\% & 84\% & 0.66 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.001_dense_dropout0.25_first_layer_filters24_kernel_size3_convolutional_layers_per_group3time1532825383_epoch88.json
            \hline
            0.001 & 0.5 & 48 & 5 & 17 & 88\% & 92\% & 73\% & 0.73 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.001_dense_dropout0.5_first_layer_filters48_kernel_size5_convolutional_layers_per_group3time1532837124_epoch0.json
            \hline
            0.0003 & 0 & 48 & 5 & 32 & 78\% & 76\% & 56\% & 0.95 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.0003_dense_dropout0_first_layer_filters48_kernel_size5_convolutional_layers_per_group6time1532846835_epoch63.json
            \hline
            0.0003 & 0.5 & 48 & 5 & 32 & 74\% & 67\% & 53\% & 0.92 \\
            % ../experimental_data/validation_results/2018_07_28_waveform_grid_search/waveform_grid_search_l2_lambda0.0003_dense_dropout0.5_first_layer_filters48_kernel_size5_convolutional_layers_per_group6time1532863869_epoch10.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of supervised learning configurations, trained with $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|}
            \hline
            Configuration & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            $DeepConvWithPos(\omega, \chi)$ & 96\% & 99\% & 96\% & 0.41 \\
            \hline
            $FourierMLP(PosCor(\beta_{8}))$ & 96\% & 98\% & 97\% & 0.42 \\
            \hline
            $FourierMLP(\beta_{8})$ & 98\% & 100\% & 98\% & 0.29 \\
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 97\% & 98\% & 98\% & 0.43 \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 94\% & 99\% & 93\% & 0.52 \\
            \hline
            $FourierMLPWithPos(\beta_{40}, \chi)$ & 91\% & 98\% & 90\% & 0.57 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 91\% & 94\% & 93\% & 0.53 \\
            \hline
            Original PICO-60 Neural Network & 83\% & 83\% & 95\% & 0.83 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of supervised learning configurations, trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|}
            \hline
            Configuration & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 93\% & 77\% & 0.63 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 97\% & 93\% & 98\% & 0.47 \\
            \hline
            $DeepConv(\omega)$ & 77\% & 76\% & 94\% & 0.86 \\
            % ../experimental_data/validation_results/2018_07_16_waveform_with_new_cuts/waveform_time1531762243_epoch14.json
            \hline
            $DeepConvWithPos(\omega, \chi)$ & 91\% & 95\% & 78\% & 0.61 \\
            \hline
            $ImageConv(\iota)$ & 85\% & 40\% & 38\% & 0.95 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}
